Problem of Step 4 (debias) of fGFPCA on NHANES data

### 2024-02-29 Docs/NhanesApplExample.Rmd
update meeting notes

Below are figures for $\hat{f}_0(t)+2\sqrt{\hat{\lambda}}_k\phi_l(k)$, but on the probablity scale

```{r}
df_pc_dev <- df_phi %>%
  mutate(mu = mu) %>%
  mutate(phi1_dev = mu + 2*sqrt(evals[1])*phi1,
         phi2_dev = mu + 2*sqrt(evals[2])*phi2,
         phi3_dev = mu + 2*sqrt(evals[3])*phi3,
         phi4_dev = mu + 2*sqrt(evals[4])*phi4)

df_pc_dev %>%
  pivot_longer(7:10) %>%
  mutate(value = plogis(value), mu = plogis(mu)) %>%
  ggplot()+
  geom_line(aes(x=sind, y=value))+
  geom_line(aes(x=sind, y=mu), col = "red")+
  facet_wrap(~name) 
```

@@

>>>>

Below are figures for $\hat{f}_0(t) \pm 2\sqrt{\hat{\lambda}}_k\phi_l(k)$, but on the probablity scale

```{r}
df_pc_dev <- bind_rows(
  data.frame(sind = 1:J, mu=mu, pc = "PC1",
             high = mu + 2*sqrt(evals[1])*df_phi$phi1,
             low = mu - 2*sqrt(evals[1])*df_phi$phi1),
  data.frame(sind = 1:J, mu=mu, pc = "PC2",
             high = mu + 2*sqrt(evals[2])*df_phi$phi2,
             low = mu - 2*sqrt(evals[2])*df_phi$phi2),
  data.frame(sind = 1:J, mu=mu, pc = "PC3",
             high = mu + 2*sqrt(evals[3])*df_phi$phi3,
             low = mu - 2*sqrt(evals[3])*df_phi$phi3),
  data.frame(sind = 1:J, mu=mu, pc = "PC4",
             high = mu + 2*sqrt(evals[4])*df_phi$phi4,
             low = mu - 2*sqrt(evals[4])*df_phi$phi4)
)

```{r}
df_pc_dev %>%
  ggplot()+
  geom_ribbon(aes(x=sind, y=mu, ymin=low, ymax=high, alpha = 0.2))+
  geom_line(aes(x=sind, y=mu))+
  facet_wrap(~pc) 
```

@@

There are a lot of flips between upper and lower bound in PC 2-4. This is certainly possible since the value of eigenfunctions can be either positive or negative. But is this an abnormal observation?
